Manuscript for a Data Analysis Project: Diabetes Diagnosis

### 2024-06-11 products/manuscript/Manuscript.qmd
Fix Links

---
title: "Manuscript for a Data Analysis Project: Diabetes Diagnosis"
subtitle: ""
author: Austin Thrash
date: today
format:
  html:
    toc: true
    toc-location: left
    number-sections: true
    highlight-style: github
bibliography: ../dataanalysis-template-references.bib
csl: ../apa.csl
---

>>>>

---
title: "Manuscript for a Data Analysis Project: Diabetes Diagnosis"
subtitle: ""
author: Austin Thrash
date: today
format:
  html:
    toc: true
    toc-location: left
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-template-references.bib
csl: ../../assets/apa.csl
---
